Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-10-11 paper/article.tex
poucas mudanças no cabeçalho. Tempo investido na configuração da VPN (o que, no final das contas, é fácil).

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
}

@@

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

>>>>

\author{\IEEEauthorblockN{Alexandro Vladno}
\IEEEauthorblockA{\textit{Centre for Informatics and Systems} \\
\textit{University of Coimbra}\\
Coimbra, Portugal \\
alexandro.vladno@gmail.com}
\and
\IEEEauthorblockN{Fabiano Papaiz}
\IEEEauthorblockA{\textit{Centre for Informatics and Systems} \\
\textit{University of Coimbra}\\
Coimbra, Portugal \\
fabianopapaiz@gmail.com}
\and
\IEEEauthorblockN{Leo Moreira Silva}
\IEEEauthorblockA{\textit{Centre of Informatics and Systems} \\
\textit{University of Coimbra}\\
Coimbra, Portugal \\
leo.moreira@me.com}
}

@@

% \begin{figure}[htbp]
% \centerline{\includegraphics{fig1.png}}
% \caption{Example of a figure caption.}
% \label{fig}
% \end{figure}
